### 2023-03-13 main.tex
DualityCheck

\section{Duality}
Consider two Markov processes $(\eta_{t})_{t\geq 0}$ on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ on a state space $\widetilde{\Omega}$. We say that they are dual, with respect to a duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$ if $\forall \eta\in \Omega$, $\forall \xi\in \widetilde{\Omega}$ and $\forall t\geq 0$ we have 
    \mathbb{E}_{\eta}\left[D(\eta_{t},\xi)\right]=\mathbb{E}_{\xi}\left[D(\eta,\xi_{t}\right]
Moreover, if $\eta_{t}$ and $\xi_{t}$ are the same process, we talk about \textit{self-duality} and \textit{self-duality function}. The duality property can also be characterized by a relation with the generators. Let $\mathcal{L}$ be the generator of $\eta_{t}$ and let $\mathcal{L}_{dual}$ be the generator of $\xi_{t}$, then we say that two process are in a duality relation if 
    \left(\mathcal{L}D(\cdot,\xi)\right)(\eta)=\left(\mathcal{L}_{dual}D(\eta,\cdot)\right)(\xi)
\subsection{Algebraic formulation}
In particular, if the process has a countable space, the duality is a matrix, and we can rewrite the above relation with the Hamiltonians has follows
\begin{equation}\label{dualityHamiltonian}
    H^{T}D=DH_{dual}
By \eqref{dualityHamiltonian}, we can see the duality matrix as a similarity transformation between the original and the dual Hamiltonian. \\
We now construct our main result: \textit{the process defined in \eqref{Generator} is self dual with absorbing boundaries}. Thus, we have to construct a duality matrix $D$ and an Hamiltonian $H_{dual}$ in order to fulfill the equation \eqref{dualityHamiltonian}.
The self-dual process is defined in the self-dual state space 
\begin{equation}\widetilde{\Omega}:=\Omega\times \mathbb{N}_{0}^{|V|}\end{equation} with elements
	|\xi\rangle=\bigotimes_{x\in V}\left(|r_{0},\ldots,r_{N}\rangle_{x}\otimes |m_{1}^{\varepsilon(x)},\ldots,m_{N}^{\varepsilon(x)}\rangle_{x}\right)
The self-dual Hamiltonian is the following
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{H}_{x,\varepsilon(x)}
\begin{align}\label{Hedge}
H_{x,y}&=\sum_{k,l=1}^{N}\left(E_{kl}^{x}\otimes E_{lk}^{y}-E_{ll}^{x}\otimes E_{kk}^{y}\right)\\
\widetilde{H}_{x,\varepsilon(x)}&=\left(\sum_{i=2}^{N}\alpha_{i}^{x}\right)\sum_{k=2}^{N}\left((a^{\dagger}_{k})_{\varepsilon(x)}E_{1k}^{x}-E_{kk}^{x}\right)
\end{align}
and where  $(a^{\dagger}_{k})_{\varepsilon(x)}$ is a bosonic creation operator acting on an extra site attached to $x$ and denoted by $\varepsilon(x)$. Let us notice that edge part of the dual Hamiltonian is exactly the one of \eqref{edgeHamiltonian} (self-duality). The site part only replace any particle of type $k\in \{2,\ldots,N\}$ with a type $1$  and put them into an extra site, attached to $x$. Dual particles of type $k$ are piled up into an this extra site, and they leave the graph forever. This means that the species $1$ plays a special role in the duality. If we think about this $1$ species as the empty, we can interpret the dual process as an absorbing dual, i.e. a process that eventually empties the graph.\\
Associated with this dual process there is the following duality matrix 

@@

	D=\prod_{x\in V}\left(\sum_{m_{2}^{\varepsilon(x)},\ldots,m_{N}^{\varepsilon(x)}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\alpha_{0}^{x}+\ldots+\alpha_{N}^{x}}\right)^{m_{k}^{\varepsilon(x)}}\langle m_{2},\ldots,m_{N}|_{\varepsilon(x)}\otimes R_{x}e^{E}_{x} \right)
	=\prod_{x\in V}\left(D_{\varepsilon(x)}\otimes D_{x}\right)
where we define the \textit{symmetry operator} as
\begin{equation}\label{e_def}
	E=\sum_{a=2}^{N}e_{a1}
and the \textit{cheap duality matrix} as 
	R^{-1}_{x}=\sum_{n\in \chi}\frac{(2j)!}{n_{1}^{x}!\ldots n_{N}^{x}!}|n_{1},\ldots,n_{N}\rangle_{x}\langle n_{1},\ldots,n_{N}|_{x}%\quad \forall n\in \chi
Moreover, the element of the matrix \eqref{dualityMatrix} are given by
	D(n,\xi)=\langle n|D|\xi\rangle=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{(2j)!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{m_{k}^{\varepsilon(x)}}\right)
\subsubsection{Proof of the duality relation}
\textbf{The transposition property of the cheap duality}: \\
This cheap duality matrix has the following \textit{transposition property}:
\begin{equation}\label{transpositionR}
	\left(e_{ba}\right)^{T}=R e_{ab}R^{-1}\quad \forall a,b\in\{0,1,\ldots,N\}
Indeed, for any configuration $\mathbf{n},\mathbf{r}\in \Omega$, by using \eqref{matrixFormulaE} we obtain
	R e_{ab}R^{-1}=&\sum_{r\in\chi}\left(\frac{r_{1}!\ldots r_{N}!}{(2j)!}|r_{1},\ldots,r_{N}\rangle \langle r_{1},\ldots, r_{N}|\right)

@@

	\sum_{s\in \chi,}\left(s_{b}|s_{1},\ldots,s_{a}+1,\ldots,s_{b}-1,\ldots s_{N}\rangle \langle s_{1},\ldots,s_{N}|\right)

@@

	\sum_{n\in\chi}\left(\frac{(2j)!}{n_{1}!\ldots n_{N}!}|n_{1},\ldots,n_{N}\rangle \langle n_{1},\ldots, n_{N}|\right)=

@@

	\sum_{r,n\in \chi}\frac{r_{1}!\ldots r_{N}!}{(2j)!}|r_{1},\ldots,r_{N}\rangle \langle r_{0},\ldots, r_{N}|
	\frac{(2j)!}{n_{1}!\ldots n_{N}!}n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots n_{N}\rangle \langle n_{1},\ldots,n_{N}|=\diamond
By using orthogonality relation \eqref{ortho}\begin{align*}
\diamond=&\sum_{r\in \chi}\frac{r_{1}!\ldots r_{N}!}{(2j)!}\frac{(2j)!}{r_{1}!\ldots (r_{a}-1)!\ldots(r_{b}+1)!\ldots r_{N}!}(r_{b}+1)|r_{1},\ldots,r_{N}\rangle \langle r_{0},\ldots,r_{a}-1,\ldots,r_{b}-1,\ldots,r_{N}|
	\\=&\sum_{r\in\chi}\frac{r_{1}!\ldots r_{N}!}{(2j)!}\frac{(2j)!}{r_{1}!\ldots (r_{a}-1)!\ldots(r_{b}+1)!\ldots r_{N}!}(r_{b}+1)\frac{r_{a}}{r_{a}}|r_{1},\ldots,r_{N}\rangle \langle r_{1},\ldots,r_{a}-1,\ldots,r_{b}-1,\ldots,r_{N}|

@@

	r_{a}|r_{1},\ldots,r_{N}\rangle \langle r_{1},\ldots,r_{a}-1,\ldots,r_{b}-1,\ldots,r_{N}|

@@

	\left(e_{ba}\right)^{T}
\textbf{The edge self-duality}\\
The second Casimir $C_{2}$ is a central element of $gl(N)$. Thus, every element of $gl(N)$ is a symmetry of $C_{2}$.
Let's chose the operator $E$ defined in \eqref{e_def}, then $\Delta(E)$ is a symmetry of $\Delta(C_{2})$.
In order to preserve a product structure of the duality matrix, we make the symmetry exponential:
\begin{equation}\label{Simmetry_s}
	S=e^{\Delta(E)}
By considering two sites $x,y$:
		S&=e^{\Delta(E)}=e^{(\mathbbm{1}\otimes E+E\otimes \mathbbm{1})}=e^{\mathbbm{1}\otimes E}e^{E\otimes \mathbbm{1}}=\sum_{k=0}^{N}\frac{\left(\mathbbm{1}\otimes E\right)^{k}}{k!}\sum_{j=0}^{N}\frac{\left(E\otimes \mathbbm{1}\right)^{j}}{j!}

@@

		\left(\mathbbm{1}\otimes \sum_{k=0}^{N}\frac{E^{k}}{k!}\right)\left(\sum_{j=0}^{N}\frac{E^{j}}{j!}\otimes \mathbbm{1}\right)=\left(\mathbbm{1}\otimes e^{E}\right)\left(e^{E}\otimes \mathbbm{1}\right)=e^{E}\otimes e^{E}
		\\&=e_{x}^{E} e^{E}_{y}
Since the Hamiltonian \eqref{OriginalHamiltonian}, can be written as a linear function of the coproduct of the second Casimir, we have \begin{equation}[H_{x,y},e^{\Delta (C_{2})}]=0\end{equation} and thus \begin{equation}\label{symmetryH-C}[H_{x,y},e^{E}_{x}e^{E}_{y}]=0\end{equation} then the operator \eqref{Simmetry_s} is also a symmetry for the Hamiltonian. 
Since the duality matrix \eqref{dualityMatrix} is product over the vertex of the graph it is enough to prove that $\forall x,y\in \mathcal{E}$:
\begin{align}
	H_{x,y}^{T}D=DH_{x,y}\label{bulkDuality}
\end{align}
For a fixed edge we only have $D_{x}D_{y}$. 
	H_{x,y}^{T}D&=D_{\varepsilon(x)}D_{\varepsilon(y)}\otimes R_{x}R_{y}H_{x,y}R_{x}^{-1}R_{y}^{-1}R_{x}R_{y}e^{E}_{x}e^{E}_{y}\prod_{z\neq x,y}D_{e(z)}D_{z}

@@

	D_{\varepsilon(x)}D_{\varepsilon(y)}\otimes R_{x}R_{y}H_{x,y}e^{E}_{x}e^{E}_{y}\prod_{z\neq x,y}D_{e(z)}D_{z}
By exploiting \eqref{symmetryH-C}
	H_{x,y}^{T}D&=	D_{\varepsilon(x)}D_{\varepsilon(y)}\otimes R_{x}R_{y}e^{E}_{x}e^{E}_{y}\prod_{z\neq x,y}D_{e(z)}\otimes D_{z}H_{x,y}=
	DH_{x,y}
thus (\ref{bulkDuality}) is proved. \\
\textbf{The site absorbing duality}\\
For the sake of notation we remove the superscripts "$x$" from the operators $E_{ab}$ and from the reservoirs densities $\alpha_{k}$. Exploiting again the product form of the duality matrix we can just show that, $\forall x\in V$ the following relation is true 
\begin{equation}\label{boundaryDuality}
    	H_{x}^{T}D=D\widetilde{H}_{x,\varepsilon(x)}
For the sake of notation and without loss of generality we restrict to the case where $N=3$. \\

>>>>

\section{Duality}
\subsection{Definition of duality}
Consider two Markov processes $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$. We say that they are dual, with respect to a duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$, if $\forall \eta\in\Omega$, $\forall \xi\in\widetilde{\Omega}$ and $\forall t> 0$ we have 
\begin{equation}
    \mathbb{E}_{\eta}\left[D(\eta_{t},\xi)\right]=\mathbb{E}_{\xi}\left[D(\eta,\xi_{t})\right]
\end{equation}
where $\mathbb{E}_{\eta}$ denotes the expectation with respect the law of the Markov process $(\eta_{t})_{t\geq 0}$ initialized with the particle configuration $\eta$, whereas $\mathbb{E}_{\xi}$ denotes the expectation with respect the law of the Markov process $(\xi_{t})_{t\geq 0}$ initialized with the particle configuration $\xi$.
The duality definition can also be formulated as a relation between the generators. Call $\mathcal{L}$ the generator of $(\eta_{t})_{t\geq0}$ and $\widetilde{\mathcal{L}}$ the generator of $(\xi_{t})_{t\geq 0}$, then we say that these two processes are dual with respect the duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$ if $\forall \eta\in\Omega$ and $\forall \xi\in\widetilde{\Omega}$ if
\begin{equation}\label{dualityRelationGenerator}
    \left(\mathcal{L}D(\cdot,\xi)\right)(\eta)=\left(\widetilde{\mathcal{L}}D(\eta,\cdot)\right)(\xi)
\end{equation}
\textbf{Remark}:
in the specific case where $\mathcal{L}=\widetilde{\mathcal{L}}$ we say that the processes are self-dual with respect to a self-duality function.
\newline
\newline
\textbf{Remark}:
when the state spaces of the dual processes is finite, the generators and the duality function are matrices with elements $\mathcal{L}(\eta,\eta^{'})$, $\widetilde{\mathcal{L}}(\xi,\xi^{'})$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta^{'}\in\Omega$ and $\xi,\xi^{'}\in \widetilde{\Omega}$. Therefore, we can write the duality relation \eqref{dualityRelationGenerator} as 
\begin{equation}
    \sum_{\eta^{'}\in\,\Omega}\mathcal{L}(\eta,\eta^{'})D(\eta^{'},\xi)=\sum_{\xi^{'}\in\, \widetilde{\Omega}}\widetilde{\mathcal{L}}(\xi,\xi^{'})D(\eta,\xi^{'})
\end{equation}
that can be read as
\begin{equation}\label{dualityIntertwines}
    \mathcal{L}D=D\widetilde{\mathcal{L}}^{T}
\end{equation}
where the superscript $T$ denotes the matrix transposition. Therefore, the duality relation \eqref{dualityIntertwines} is an intertwining transformation between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}$. Working with the Hamiltonian operators the duality relation \eqref{dualityIntertwines} reads as
\begin{equation}\label{DualityRelation}
    H^{T}D=D\widetilde{H}
\end{equation}
where $\widetilde{H}=\widetilde{\mathcal{L}}^{T}$.
\subsection{Duality for the generalized multi-species boundary driven stirring process}
We now state our duality result. The process $|n\rangle$ with Hamiltonian \eqref{} is dual in the sense of \eqref{DualityRelation}, with respect to a process $|\xi\rangle$ defined on the enlarged state space
\begin{equation}
    \widetilde{\Omega}:=\Omega\times \mathbb{N}_{0}^{V}
\end{equation}
with elements
\begin{equation}
    |\xi\rangle=\bigotimes_{x\in V}\left(|r_{1}^{x},\ldots,r_{N}^{x}\rangle\otimes |m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}\rangle\right)
\end{equation}
where $r_{x}^{k}$ denotes the number of dual particles of type $k\in \{1,\ldots,N\}$ at site $x\in V$ and $m_{k}^{\widetilde{x}}$ denotes the number of particles of species $k\in \{2,\ldots,N\}$ at an extra-site $\widetilde{x}$ connected to the site $x\in V$.\\
The Hamiltonian of the dual process reads as
\begin{equation}\label{DualHamiltonian}
    \widetilde{H}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{H}_{x}
\end{equation}

where $H_{x,y}$ is the one defined in \eqref{edgeHamiltonian}, while 
\begin{equation}\label{siteDualHamiltonian}
    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left((a^{\dagger})_{k}^{\widetilde{x}}\,E_{1k}^{x}-E_{kk}^{x}\right)
By introducing the action of a bosonic creation operator $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, we define in \eqref{siteDualHamiltonian} 
$(a^{\dagger})_{k}^{\widetilde{x}}$ as a copy of $a^{\dagger}$ acting on the extra-site $\widetilde{x}$ and on the species $k\in\{2,\ldots,N\}$. \\
The Hamiltonians \eqref{Hamiltonian} and \eqref{DualHamiltonian} are dual with respect to the duality matrix $D$ defined as 
    D=\bigotimes_{x\in V}\left(D_{x}\otimes D_{\widetilde{x}}\right)
We denote by $D_{x}$ the site part. This is defined as 
    D_{x}=R_{x}\exp{(E^{x})}
with $E$
    E^{x}=\sum_{k=2}^{N}E_{k1}^{x}
that implies 
    \exp{(E^{x})}=I+E^{x}
and where $R_{x}$ is the diagonal matrix with elements (up to a finite constant) the inverse of the masses of the reversible measure \eqref{reversibleMeasure}, i.e. 
    R_{x}=\sum_{n\in\chi}\frac{\prod_{k=1}^{N}n_{k}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
where, for all $x\in V$, we call $\chi=\{(n_{k}^{x})_{k\in\{1,\ldots,N\}}\in \mathbb{N}_{0}\,:\, \sum_{k=1}^{N}n_{k}^{x}=\nu\}$ the simplex.\\ 
We denote by $D_{\widetilde{x}}$ the extra-site part. It is defined as

@@

D_{\widetilde{x}}=\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
On one hand, the edge part of the dual Hamiltonian \eqref{DualHamiltonian} is a copy of \eqref{edgeHamiltonian}, therefore it performs the stirring dynamic on the graph. On the other hand, the site dual Hamiltonian \eqref{siteDualHamiltonian} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\widetilde{x}$. This means that, eventually, only particles of type $1$ remain in the graph while all other types are absorbed by the extra-sites. Thinking about the type $1$ as the hole, similarly to what happens in the SEP(2j)\cite{GioaGiardinaGibertiFrank}, the graph is eventually emptied. 
\subsection{Proof of the duality relation}\label{subsectionDualityProof}
To prove the duality relation between \eqref{} and \eqref{DualHamiltonian} with the duality matrix \eqref{dualityMatrix} we shall show that 
    H^{T}D=D\widetilde{H}
Since the duality matrix is a tensor product over the sites $x\in V$ it is enough to prove that for the edge Hamiltonians
\begin{equation}\label{edgeDualRealtion}
    H_{x,y}^{T}D=DH_{x,y}\qquad \forall x,y\in \mathcal{E}
and for the site Hamiltonians 
\begin{equation}\label{siteDualRelation}
    H_{x}^{T}D=D\widetilde{H}_{x}\qquad \forall x\in V.
%The key idea behind the proof of \eqref{edgeDualRealtion} is that it is possible to write the Hamiltonian \eqref{} as a function of the second Casimir of the $gl(N)$ Lie algebra. Finding a symmetry $S$ of this element, will imply of having a symmetry of the Hamiltonian. By the reversibility of the process one can make $S$ act on a proper matrix (called cheap duality) and obtain 
\paragraph{Proof of \eqref{edgeDualRealtion}}
The proof of the edge duality relation relies on two facts: first the existence of a diagonal matrix, arising from the reversible measure, that is already a duality for the Hamiltonian (in literature called 'cheap' duality matrix, see \cite{}); second the possibility of finding a proper symmetry of the Hamiltonian.  \\We first introduce the cheap duality matrix 
\begin{equation}\label{transpositionPropertyR}
R_{x}=\sum_{n\in\chi}\frac{\prod_{k=1}^{N}n_{k}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
This is diagonal with the inverse of the masses of the reversible measure \eqref{reversibleMeasure}. 
This matrix connects the generators of the algebra $E^{x}_{ab}$ with their transposed $(E_{ab}^{x})^{T}$ by the following relation
(E_{ab}^{x})^{T}=R_{x}E_{ab}^{x}R_{x}^{-1}\qquad \forall x\in V
Indeed, we have
RE_{ab}^{x}R^{-1}=&\sum_{r\in\chi}\left(\frac{r_{1}^{x}!\ldots r_{N}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots, r_{N}^{x}|\right)

@@

	\sum_{s\in \chi,}\left(s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|\right)

@@

	\sum_{n\in\chi}\left(\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|\right)
	\sum_{r,n\in \chi}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{0}^{x},\ldots, r_{N}^{x}|
	\frac{\nu!}{n_{1}^{x}!\ldots n_{N}^{x}!}n_{b}^{x}

@@

 \qquad |n_{1}^{x},\ldots,n_{a}^{x}+1,\ldots,n_{b}^{x}-1,\ldots n_{N}^{x}\rangle \langle n_{1}^{x},\ldots,n_{N}^{x}|
 \sum_{r\in \chi}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}\frac{\nu!}{r_{1}^{x}!\ldots (r_{a}^{x}-1)!\ldots(r_{b}^{x}+1)!\ldots r_{N}^{x}!}(r_{b}^{x}+1)
 \\&\qquad
 |r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{0}^{x},\ldots,r_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,r_{N}^{x}|
	\\=&\sum_{r\in\chi}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}\frac{\nu!}{r_{1}^{x}!\ldots (r_{a}^{x}-1)!\ldots(r_{b}^{x}+1)!\ldots r_{N}^{x}!}(r_{b}^{x}+1)\frac{r_{a}^{x}}{r_{a}^{x}}
 \\& \qquad
 |r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots,r_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,r_{N}^{x}|

@@

	r_{a}^{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots,r_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,r_{N}^{x}|

@@

	\left(E_{ba}^{x}\right)^{T}
where in the third to last equation we multiplied and divided for $r_{a}^{x}$. 
The relation \eqref{transpositionPropertyR} implies that 
    H_{x,y}^{T}=\left(R_{x}\otimes R_{y}\right)H_{x,y}\left(R_{x}\otimes R_{y}\right)^{-1}
We now look for a symmetry of the Hamiltonian. As shown in \eqref{}, it is possible to write the Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the second Casimir of $gl(N)$. We say that a matrix $A\in gl(N)$ is symmetry of the Casimir $C_{2}$ if
    [A,C_{2}]=0
By the definition of the standard coproduct operator, it is possible to show that
    [A,C_{2}]=0\qquad \Longrightarrow \qquad \left[\Delta(A),\Delta(C_{2})\right]=0
 $C_{2}$ is a central element of $gl(N)$, then it commutes with every element of the algebra. 
We chose as a symmetry 
\begin{equation}\label{equationE}
    E^{x}=\sum_{k=2}E_{a1}^{x}
As a consequence of the previous considerations we can state that $E^{x}$ is a symmetry for the Hamiltonian \eqref{edgeHamiltonian}. We take the exponential of this symmetry by introducing
\begin{equation}\label{symmetry}
    S_{x,y}=\exp{(\Delta(E^{x}))}
This operator can be rewritten as 
		S&=e^{\Delta^{x,y}(E)}=\exp{(\mathbbm{1}^{x}\otimes E^{y}+E^{x}\otimes \mathbbm{1}^{y})}=\exp{(\mathbbm{1}^{x}\otimes E^{y})} \exp{(E^{x}\otimes \mathbbm{1}^{y})}\\&=\sum_{k=0}^{N}\frac{\left(\mathbbm{1}^{y}\otimes E^{x}\right)^{k}}{k!}\sum_{j=0}^{N}\frac{\left(E^{x}\otimes \mathbbm{1}^{y}\right)^{j}}{j!}=
		\left(\mathbbm{1}^{x}\otimes \sum_{k=0}^{N}\frac{(E^{y})^{k}}{k!}\right)\left(\sum_{j=0}^{N}\frac{(E^{x})^{j}}{j!}\otimes \mathbbm{1}^{y}\right)\\&=\left(\mathbbm{1}^{x}\otimes \exp{({E}^{y})}\right)\left(\exp{(E^{x})}\otimes \mathbbm{1}^{y}\right)\\&=\exp{(E^{x})}\otimes \exp{(E^{y})}
Moreover, by the exponential series of \eqref{equationE}, we have 
   \exp{(E^{x})}\otimes \exp{(E^{y})}= \left(\mathbbm{1}^{x}+E^{x}\right)\otimes \left(\mathbbm{1}^{y}+E^{y}\right)
Since \eqref{equationE} is a symmetry for $C_{2}$, then we have that
\begin{equation}\label{commutationSymm-edgeHamiltonian}
\left[H_{x,y},S\right]=\left[H_{x,y},\exp{(E^{x})}\otimes \exp{(E^{y})}\right]=0
By using \eqref{transpositionPropertyR} and \eqref{commutationSymm-edgeHamiltonian} we obtain
        H_{x,y}^{T}D=&\left(R_{x}\otimes R_{y}\right)H_{x,y}\left(R_{x}\otimes R_{y}\right)^{-1}D
        \left(R_{x}\otimes R_{y}\right)H_{x,y}\left(R_{x}\otimes R_{y}\right)^{-1}\left(R_{x}\otimes R_{y}\right)
        \left(\left(\exp{(E^{x})}\otimes D_{\widetilde{x}}\right)\otimes \left(\exp{(E^{y})}\otimes D_{\widetilde{y}}\right)\right)\bigotimes_{z\in V\,:\,z\neq x,y}(D_{z}\otimes D_{\widetilde{z}})
        \left(R_{x}\otimes R_{y}\right)H_{x,y}\left(\left(\exp{(E^{x})}\otimes D_{\widetilde{x}}\right)\otimes \left(\exp{(E^{y})}\otimes D_{\widetilde{y}}\right)\right)\bigotimes_{z\in V\,:\,z\neq x,y}(D_{z}\otimes D_{\widetilde{z}})
    \left(\left(R_{x}\exp{(E^{x})}\otimes D_{\widetilde{x}}\right)\otimes \left(R_{y}\exp{(E^{y})}\otimes D_{\widetilde{y}}\right)\right)H_{x,y}\bigotimes_{z\in V\,:\, z\neq x,y}\left(D_{z}\otimes D_{\widetilde{z}}\right)
    D H_{xy}
therefore \eqref{edgeDualRealtion} is proved. 
\paragraph{Proof of \eqref{siteDualRelation}} The proof of the site duality relations relies on the Hadamard Lemma that, $\forall E,A \in gl(N)$, reads as 
\begin{equation}\label{HadamardFormula}
    \exp{(-E)}A\exp{(E)}=A-\left[E,A\right]+\frac{1}{2!}\left[E,\left[E,A\right],\right]-\frac{1}{3!}\left[E,\left[E,\left[E,A\right]\right]\right]+\ldots
 By \eqref{transpositionPropertyR} we write the transpose of site Hamiltonian \eqref{siteHamiltonian} 
H_{x}^{T}=\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{kl}^{x}-E_{ll}^{x}\right)^{T}=R_{x}\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)R_{x}^{-1}
we multiply both sides for $R_{x}\exp{(E^{x})}$
    H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{k,\ell=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)R_{x}^{-1}R_{x}\exp{(E^{x})}=R_{x}\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}
we insert the identity $I=\exp{(E^{x})}\exp{(-E^{x})}$ in the right hand side
\begin{equation}\label{intermediateTransposeSite}
H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\exp{(-E^{x})}\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}
we apply the Hadamard's formula \eqref{HadamardFormula} to 
    \exp{(-E^{x})}\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}
We compute the following quantities by the commutation relations \eqref{}:
    \item for all $k\neq 1$ 
        \exp{(-E^{x})}E_{k1}^{x}\exp{(E^{x})}=E_{k1}^{x},
    \exp{(-E^{x})}E_{kk}^{x}\exp{(E^{x})}=E_{kk}^{x}+E_{k1}^{x}
    \exp{(-E^{x})}E_{1k}^{x}\exp{(E^{x})}=E_{1k}^{x}+E_{11}^{x}-\sum_{a=2}^{N}\left(E_{a1}^{x}+E_{ak}^{x}\right)
Indeed we have the following commutators at the first order:
\sum_{a=2}^{N}\left[E_{a1}^{x},E_{kk}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{k1}-E_{k1}^{x}\delta_{ak}\right)
\sum_{a=2}^{N}\left[E_{a1}^{x},E_{1k}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{11}-E_{11}^{x}\delta_{ak}\right)=\sum_{a=2}^{N}E_{ak}^{x}-E_{11}^{x};
and the following commutators at the second order:
&\sum_{b=2}^{N}\sum_{a=2}^{N}\left[E_{b1}^{x},E_{ak}^{x}\right]-\sum_{b=2}^{N}\left[E_{b1}^{x},E_{11}^{x}\right]=\sum_{a,b=2}^{N}\left(E_{bk}^{x}\delta_{a1}-E_{a1}^{x}\delta_{bk}\right)-\sum_{b=2}^{N}\left(E_{b1}\delta_{11}-E_{11}\delta_{b1}\right)\\=&-2\sum_{a=2}^{N}E_{a1}^{x};
from the third on-wards all commutators zero. 
\item for all $k,l\neq 1$
    \exp{(-E^{x})}E_{lk}^{x}\exp{(E^{x})}=E_{kl}^{x}+E_{l1}^{x}
Indeed the first commutator gives
\sum_{a=2}^{N}\left[E_{a1}^{x},E_{lk}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{l1}-E_{l1}^{x}\delta_{ak}\right)=-E_{l1}^{x};
and the from the second commutator on-wards they are all zero.
\item for the matrix $E_{11}^{x}$
    \exp{(-E^{x})}E_{11}^{x}\exp{(E^{x})}=E_{11}^{x}-\sum_{a=2}^{N}E_{a1}^{x}
indeed the first commutator gives
\sum_{a=2}^{N}\left[E_{a1}^{x},E_{lk}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{11}-E_{l1}^{x}\delta_{a1}\right)=\sum_{a=2}^{N}E_{a1}^{x};
and the from the second commutator on-wards they are all zero.
Therefore we have
    &\exp{(-E^{x})}\sum_{k=1}^{N}\sum_{l=1}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}\\&=
     \exp{(-E^{x})}\sum_{k=1}^{N}\alpha_{k}^{x}\left(E_{1k}^{x}-E_{11}^{x}\right)\exp{(E^{x})}
     + \exp{(-E^{x})}\sum_{k=1}^{N}\sum_{l=2}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}

@@

     \sum_{k=1}^{N}\alpha_{k}^{x}\left(E_{1k}+E_{11}^{x}-\sum_{a=2}^{N}(E_{jk}^{x}+E_{l1}^{x})-E_{11}^{x}+\sum_{j=2}^{N}E_{j1}^{x}\right)+\sum_{k=1}^{N}\sum_{l=2}^{N}\left(E_{lk}^{x}+E_{\ell 1}^{x}-E_{\ell\ell}^{x}-E_{l1}^{x}\right)

@@

     \sum_{k=1}^{N}\alpha_{k}^{x}\left(E_{1k}^{x}-\sum_{j=2}^{N}E_{jj}^{x}\right)
Thus, multiplying and dividing by $\sum_{i=1}^{N}\alpha_{i}^{x}$, we rewrite \eqref{intermediateTransposeSite} as
\begin{equation}\label{siteHadamardI}
H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\left(E_{1k}^{x}-\sum_{j=2}^{N}E_{jj}\right)
We multiply both sides of \eqref{siteHadamard} by 
